Fluent statistical computing interfaces for biological data analysis

### 2020-08-03 Rmd/05-embeddings.Rmd
update reference
adjust fig sizes

We *strongly* recommend viewing the linked videos for each case study
while reading. The videos are available to view online from the links
in the captions of each sections figures. The videos presented show the visual 
appearance of the **liminal** interface, and how we can interact with the tour
via the controls previously described. If you are unable to view the videos,
the figures in each case study consist of screenshots that summarise what is
learned from combining the tour and an embedding view.

@@

(ref:liminal-gaussian) Screenshots of the **liminal** interface applied to well clustered data, a video of the tour animation is available at https://player.vimeo.com/video/439635921. *(a)*: t-SNE (left) and tour (right) in side by side layout coloured by cluster. *(b)*: brushing the red cluster on the t-SNE view, shows the corresponding points on the tour.

```{r gaussian, fig.cap = "(ref:liminal-gaussian)"}
display_screenshot("gaussian", vid_lookup)
```

@@

(ref:liminal-hierarchical) Screenshots of the **liminal** interface applied to sub-clustered data, a video of the tour animation is available at https://player.vimeo.com/video/43963590. *(a)* t-SNE has identified and spread out the clusters with substructure. *(b)* Using linked highlighting and brushing, the tour view shows that sub-clusters are much closer together in high dimensional space than the t-SNE view implies.

```{r hierarchical, fig.cap="(ref:liminal-hierarchical)"}
display_screenshot("hierarchical", vid_lookup)
```

@@

(ref:trees-01) Screenshots of the **liminal** interface applied to tree structured data, a video of the tour animation is available at https://player.vimeo.com/video/439635892. *(a)*: Default t-SNE has difficulties embedding the tree. *(b)* linked highlighting shows that the backbone of the tree has been broken by the embedding.

```{r trees-01, fig.cap = "(ref:trees-01)"}
display_screenshot("trees-01", vid_lookup)
```

@@

(ref:mouse-01) Screenshots of the **liminal** interface applied to single cell data. A video of the tour animation is available at https://player.vimeo.com/video/439635812. *(a)*: linked brushing identifies distortions in cluster placement by the embedding. *(b)*: t-SNE spreads out larger clusters like cluster 2, 4, 6, and 11 which are concentrated in the tour view. *(c)*: the tour view gives a sense of the geometry of the data; the PCs appear to form a tetrahedron like shape. *(d)*: brushing on the tour view highlights diffusions, points in cluster 9 are close together in the tour view are far away in the t-SNE view.

```{r mouse-01, fig.cap = "(ref:mouse-01)" }
display_screenshot("mouse-01", vid_lookup)
```

@@

(ref:mouse-02) Screenshots of the **liminal** tour applied to a marker gene set. A video of the tour animation is available at https://player.vimeo.com/video/439635843. *(a)*: the axis (left) and tour (right) view of 10 marker genes, using linked highlighting we see that the marker genes separate clusters 2, 4, 6, and 11 from the other groups. *(b)*: after zooming, it appears that the marker genes give rise to a gradient along the clusters.

```{r mouse-02, fig.cap = "(ref:mouse-02)"}
display_screenshot("mouse-02", vid_lookup)
```

>>>>

We *strongly* recommend viewing the linked videos for each case study
while reading. Links to the videos are available in table \@ref(tab:vimeo) 
and in the figures for each case study. The videos presented show the visual 
appearance of the **liminal** interface, and how we can interact with the tour
via the controls previously described. If you are unable to view the videos,
the figures in each case study consist of screenshots that summarise what is
learned from combining the tour and an embedding view.

@@

(ref:liminal-gaussian) Screenshots of the **liminal** interface applied to well clustered data, a video of the tour animation is available at https://player.vimeo.com/video/439635921.

```{r gaussian, fig.cap = "(ref:liminal-gaussian)", out.height = "75%"}
display_screenshot("gaussian", vid_lookup)
```

@@

(ref:liminal-hierarchical) Screenshots of the **liminal** interface applied to sub-clustered data, a video of the tour animation is available at https://player.vimeo.com/video/43963590.

```{r hierarchical, fig.cap="(ref:liminal-hierarchical)", out.height = "75%"}
display_screenshot("hierarchical", vid_lookup)
```

@@

(ref:trees-01) Screenshots of the **liminal** interface applied to tree structured data, a video of the tour animation is available at https://player.vimeo.com/video/439635892.

```{r trees-01, fig.cap = "(ref:trees-01)", out.height = "75%" }
display_screenshot("trees-01", vid_lookup)
```

@@

(ref:mouse-01) Screenshots of the **liminal** interface applied to single cell data, a video of the tour animation is available at https://player.vimeo.com/video/439635812.

```{r mouse-01, fig.cap = "(ref:mouse-01)", out.height = "75%"}
display_screenshot("mouse-01", vid_lookup)
```

@@

(ref:mouse-02) Screenshots of the **liminal** tour applied to a marker gene set, a video of the tour animation is available at https://player.vimeo.com/video/439635843.

```{r mouse-02, fig.cap = "(ref:mouse-02)", out.height = "75%"}
display_screenshot("mouse-02", vid_lookup)
```
